---
title: "R Notebook"
output: html_notebook
---


```{r}
library(dplyr)
library(ggplot2)
library(cowplot)
library(sharpr2)

options(stringsAsFactors = F, scipen = 1000)

data_raw <- read.table('../processed_data/HiDRA_frag_all.txt', header = T) %>% 
    arrange(start)

data_rep1 <- data_raw %>% 
    select(start, end, PLASMID =  DNA_1, RNA = RNA_1)

data_rep2 <- data_raw %>% 
    select(start, end, PLASMID = DNA_2, RNA = RNA_2)

data_avg <- data_raw %>% 
    select(start, end, PLASMID = DNA_ave, RNA = RNA_exp_ave)
```

```{r}
ggplot(data_raw, aes(RNA_exp_ave)) + 
    geom_histogram(binwidth = 0.1) + xlim(c(-1, 100)) + scale_x_log10() +
    geom_vline(xintercept = 0.05)
```

```{r}
ggplot(data_raw, aes(DNA_ave)) + 
    geom_histogram(binwidth = 0.1) + xlim(c(-1, 100)) + scale_x_log10() +
    geom_vline(xintercept = 0.10)
```

Default arguments for sharpr2:
- `l_min = 150`, fragments less than 150bp not considered
- `l_max = 499`, fragments longer than 499bp not considered
- `f_rna = 10`, fragments with RNA count less than 10 not considered.
- `f_dna = 0`, fragments with DNA count less than 0 not considered
- `len = FALSE`, An indicator of whether to model log(RNA/PLASMID) of each fragment as the
average or the sum of the latent regulatory scores. The default is FALSE, which
is the sum.

```{r}
data(hidra_ex)
re <- sharpr2(hidra_ex, l_min = 150, l_max = 600, f_dna = 5, f_rna = 0, 
              sig=FALSE, verbose = T)
tiled_ex <- call_tile_reg(hidra_ex)
```

```{r}
tiled <- call_tile_reg(data_avg)
tiles <- data.frame(size = tiled$size)
```

```{r}
ggplot(tiles, aes(size)) + geom_histogram()
```

```{r}
result <- sharpr2(data_avg, f_dna = 0.10, f_rna = 0.05, sig = F, verbose = T, auto = F)
```


